Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-01-24 manuscript.tex
Fix typos in tikz plots

    % draw a periodic orbit
    \coordinate (center) at (0,0,2);
    \node[below right] (x0) at (0,2,2) {\(\vecbf{x}_0\)};
    \filldraw (0,2,2) circle (3pt);

    \node[below right] (x1) at (0,3,2) {\(\vecbf{x}_1\)};
    \filldraw (0,3,2) circle (3pt);

@@

        % draw a periodic orbit
        \coordinate (center) at (0,0,2);
        \node[label=below:\(\vecbf{x}_0\)] (x0) at (0,3,2) {};
        % \node[label=below:\(\vecbf{x}_n\)] at (x0) {};
        \filldraw (x0) circle (3pt);

@@

The optimal control formulation presented in this section results in a two point boundary value problem (TPBVP). 
There exist many methods to solve TPBVPs such as gradient, quasilinearization, and shooting methods~\cite{bryson1975,kirk2012}.
Shooting methods are common in astrodynamic trajectory design problems and relatively simple to implement.
In the shooting method, initial conditions are varied such that a terminal constraint is satisfied, similar to the way an archer modifies the bow in order to more accurately strike a target. 
Consider the vector of initial conditions, \( \vecbf{\chi} = \braces{\vecbf{x}_0, \vecbf{\lambda}_0}\), which is varied to satisfy some terminal constraints of the form \( \vecbf{G}(\vecbf{\chi}) = \braces{\vecbf{x}_t - \vecbf{x}_n} = 0 \).
The free variables at the terminal time are computed by propogation of \( \vecbf{\chi} \) over the selected time horizon. 
At the terminal time, the constraint vector is calculated and if not satisfied \( \vecbf{\chi}\) is varied.
Rather than numerical integration over the entire time interval, multiple shooting segments the interval into several smaller sub-arcs~\cite{stoer2013}.
The multiple shooting method is implemented in this paper which alleviates many of the issues associated with single shooting approaches.

@@

In~\cref{fig:multiple shooting}, we show a schematic representation of the multiple shooting procedure.
We split the optimal control horizon into equal length subsegments such that the length of each segment is \( \frac{k}{n} \), where \( k, n \) are the total number of steps and number of stages, respectively.
Similarly, we divide the state and costate trajectories into \( n \) equal segments. 
To ensure continuity, additional interior constraints are incorporated as
\begin{subequations}
\begin{align}\label{eq:interior_constraints}
	\vecbf{x}_1^{-} - \vecbf{x}_1^{+} &= 0 , \\ 
	\vecbf{\lambda}_1^{-} - \vecbf{\lambda}_1^{+} &= 0 , \\
	\vecbf{x}_2^{-} - \vecbf{x}_2^{+} &= 0 , \\ 
	\vecbf{\lambda}_2^{-} - \vecbf{\lambda}_2^{+} &= 0 , \\
	&\vdots \\
	\vecbf{x}_{n-1}^{-} - \vecbf{x}_{n-1}^{+} &= 0 , \\ 
	\vecbf{\lambda}_{n-1}^{-} - \vecbf{\lambda}_{n-1}^{+} &= 0.
\end{align}
\end{subequations}
Using the multiple shooting method reduces the sensitivity of the terminal states, \( \vecbf{x}_i^{+}, \vecbf{\lambda}_i^{+}\), to variations of the initial states, \(\vecbf{x}_{i-1}^{-}, \vecbf{\lambda}_{i-1}^{-}\).
As a result, the design vector \( \vecbf{\chi} \) is augmented with the additional interior initial conditions, \( \vecbf{x}_i^{-}, \vecbf{\lambda}^{-}\).
Similarly, the constraint vector is augmented with the additional interior constraints defined in~\cref{eq:interior_constraints}.
The multiple shooting algorithm now varies the design vector \( \vecbf{\chi}\) to ensure that the constraints in \( \vecbf{G}(\vecbf{\chi}) \) are satisfied.
In this work, we use the Matlab nonlinear solver \texttt{fsolve} to solve the system of nonlinear equations defined by the multiple shooting algorithm.

@@

From the initial state on the periodic orbit, a series of optimal trajectories are generated to determine the reachable set.
The multiple shooting approach is implemented to sovle the optimal control problem. 
We divide the time horizon into two equal length segments. 
The state trajectory is intialized using the free trajectory of the periodic orbit. 
Similarly, the costate trajectory is initialized from an initial guess of \( \vecbf{\lambda}_0 = \begin{bmatrix} -1 & -1 & -1 & -1\end{bmatrix}^T\) and propogated using the discrete equations of motion in~\cref{eq:costate_update}.
This results in the initial guess of the design vector \( \vecbf{\chi} = \begin{bmatrix} \vecbf{\lambda}_0 & \vecbf{x}_1^{-} & \vecbf{\lambda}_1^{-} & \vecbf{\beta} \end{bmatrix}^T\).
This design vector is then varied to ensure that the necessary conditions of optimality and the interior point constraints are satisfied.

By varying the angle \( \theta_d\) in~\cref{eq:constraints}, a different direction along the \Poincare section is maximized. 
We discretely vary the angle over the range \( \ang{0} \leq \theta_d < \ang{360} \) to approximate the reachability set of the spacecraft.
Choosing a new angle \( \theta_d \) corresponds to a different direction as well as a new optimal control problem which is again solved using the multiple shooting approach laid out previously.
The intersection of the optimal trajectories as well as those of the target Moon orbit with the \Poincare section are shown in~\cref{fig:invariant_manifold_transfer}.

>>>>

    % draw a periodic orbit
    \coordinate (center) at (0,0,2);
    \node[below right] (x0) at (0,2,2) {\(\vecbf{q}_0\)};
    \filldraw (0,2,2) circle (3pt);

    \node[below right] (x1) at (0,3,2) {\(\vecbf{q}_1\)};
    \filldraw (0,3,2) circle (3pt);

@@

        % draw a periodic orbit
        \coordinate (center) at (0,0,2);
        \node[label=below:\(\vecbf{x}_n\)] (x0) at (0,3,2) {};
        % \node[label=below:\(\vecbf{x}_n\)] at (x0) {};
        \filldraw (x0) circle (3pt);

@@

The optimal control formulation presented in this section results in a two point boundary value problem (TPBVP). 
There exist many methods to solve TPBVPs such as gradient, quasilinearization, and shooting methods~\cite{bryson1975,kirk2012}.
Shooting methods are common in astrodynamic trajectory design problems and relatively simple to implement.
In the shooting method, initial conditions are varied such that a terminal constraint is satisfied, similar to the way an archer modifies the bow in order to more accurately strike a target. 
Rather than numerical integration over the entire time interval, multiple shooting segments the interval into several smaller sub-arcs~\cite{stoer2013}.
The multiple shooting method is implemented in this paper which alleviates many of the issues associated with single shooting approaches.

@@

In~\cref{fig:multiple shooting} we show a schematic representation of the multiple shooting procedure.
We split the optimal control horizon into equal length subsegments such that the length of each segment is \( \frac{k}{n} \), where \( k, n \) are the total number of steps and number of stages, respectively.
Similarly, we divide the state and costate trajectories into \( n \) equal segments. 
To ensure continuity, additional interior constraints are incorporated as
\begin{subequations}
\begin{align}\label{eq:interior_constraints}
	\vecbf{x}_1^{-} - \vecbf{x}_1^{+} &= 0 , \\ 
	\vecbf{\lambda}_1^{-} - \vecbf{\lambda}_1^{+} &= 0 , \\
	\vecbf{x}_2^{-} - \vecbf{x}_2^{+} &= 0 , \\ 
	\vecbf{\lambda}_2^{-} - \vecbf{\lambda}_2^{+} &= 0 , \\
	&\vdots \\
	\vecbf{x}_{n-1}^{-} - \vecbf{x}_{n-1}^{+} &= 0 , \\ 
	\vecbf{\lambda}_{n-1}^{-} - \vecbf{\lambda}_{n-1}^{+} &= 0.
\end{align}
\end{subequations}
Using the multiple shooting method reduces the sensitivity of the terminal states, \( \vecbf{x}_i^{+}, \vecbf{\lambda}_i^{+}\), to variations of the initial states, \(\vecbf{x}_{i-1}^{-}, \vecbf{\lambda}_{i-1}^{-}\).
The constraints to be satisfied are defined by~\cref{eq:interior_constraints,eq:necc_cond} through selection of \( \vecbf{\lambda}_0, \vecbf{\beta}, \vecbf{x}_i^{+}, \text{ and } \vecbf{\lambda}_i^{+} \).

@@

From the initial state on the periodic orbit, a series of optimal trajectories are generated to determine the reachable set.
By varying the angle \( \theta_d\) in~\cref{eq:constraints}, a different direction along the \Poincare section is maximized. 
We discretely vary the angle over the range \( \ang{0} \leq \theta_d < \ang{360} \) to approximate the reachability set of the spacecraft.
The intersection of the optimal trajectories as well as those of the target Moon orbit with the \Poincare section are shown in~\cref{fig:invariant_manifold_transfer}.
